\huge Tor's Usability for Censorship Circumvention

### 2016-04-08 pets2017-paper/pets2017-paper.tex
Should ack TB devs (apart from Georg).

\section {Acknowledgments}
{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabella Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}

>>>>

\section {Acknowledgments}
{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabella Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.} 
{\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}
